\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-12 paper/experiments.tex
paper: added queries for fcc to experiments section

\todo{describe further queries on other data set}

\begin{table*}
  \centerfloat
  \input{queries}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table*}

>>>>

In Query~\ref{q4}, we calculate the average income for survey participants,
based on their bootcamp attendance. Query~\ref{q5} estimates the average
age of women from the Uniter States who participated. Query~\ref{q6} 
calculates the average amount of money survey participants with student debt destined to
learning based on their school degree. Finally, in Query~\ref{q7}, we join the FCC data with a reference table provided
by the World Bank which summarizes GDP per Capita across various
countries\cite{worldbank-data}. The query calculates the average GDP-per-capita for participants based on whether or not they
attended a bootcamp.

Note that for all queries we have enumerated strings and encoded them with
an appropriate integer value.

\begin{table}
\centering
 \begin{subtable}{\linewidth}
  \input{queries-cdc}
  \caption{Queries on CDC data}
  \label{fig:queries-cdc}
 \end{subtable}
 ~
 \begin{subtable}{\linewidth}
 \input{queries-fcc}
 \caption{Queries on FCC data}
 \label{fig:queries-fcc}
 \end{subtable}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table}
